---
title: "Bayesian meta-regression models for the estimation of population trends in health risk factors"
subtitle: "<span style = 'font-style: normal;'>Annibale Cois </span><span style = 'font-size: 50%;'>MEng, MPH, PhD</span>"
author: "<span style='font-size: 80%; font-style:normal;'>Division of Health Systems & Public Health, Department of Global Health, Stellenbosch University &amp; <br/> Division of Epidemiology & Biostatistics, School of Public Health, University of Cape Town</span>" 
date: "<span style = 'color: #000000; position: relative; top: 180px; font-style:normal;'>01/12/2022 &bull; George &bull; Western Cape &bull; South Africa </span>" 
output:  
  xaringan::moon_reader:
    css: ["default", "assets/sydney-fonts.css", "assets/sydney.css", "assets/stellenbosch.css"]
    self_contained: false # if true, fonts will be stored locally
    seal: true # show a title slide with YAML information
    includes:
      in_header: "assets/mathjax-equation-numbers.html"
    nature:
      beforeInit: ["assets/remark-zoom.js", "assets/cols_macro.js", "assets/macros.js"]
      highlightStyle: github
      highlightLines: true
      ratio: '16:9' # alternatives '16:9' or '4:3' or others e.g. 13:9
      countIncrementalSlides: true
      navigation:
        scroll: false # disable slide transitions by scrolling
---

class: hide_logo

```{r setup, echo=FALSE}
knitr::read_chunk('assets/init.R')
```

```{r, echo=FALSE, cache=FALSE, message=FALSE}
<<init>>
```

## Outline `r top_icon("list")`
.purple[
- ### Quantifying trends and distribution of risk factors for health
- ### Alcohol consumption as a case in point: mainstream estimation methods  
]
--
.black[
- ### Why Bayes? A principled approach to data synthesis
- ### A Bayesian meta-regression model for alcohol consumption
]
--
.black[
- ### Results: a (brief) summary
- ### Conclusion
]

???
- Quantifying trends and distribution of risk factors for health
- Alcohol consumption as a case in point: mainstream estimation methods  

- Why Bayes? A principled approach to data synthesis
- A Bayesian meta-regression model for alcohol consumption: overview, implementation, fitting, checking

- Results: a (brief) summary
- Conclusion


---
## Risk factors distributions and trends  `r top_icon("stethoscope")`


---
## Estimating alcohol consumption  `r top_icon("wine-bottle")`


---
## The WHO approach  `r top_icon("wine-bottle")`



---
## Why Bayes?  `r top_icon("circle")`


---
## A meta-regression model  `r top_icon("code")`



---
class: middle 
## `r top_icon("divide")`

 .font140[
$$\require{color}\displaystyle
\begin{align}
&L = \color{#FF0000}{\prod pc_{s,g,a,k}\cdot ne_{s,g,a}} \cdot L^{'}_{s,g,a,k} \prod L^{''}_{s,g,a}\label{EQ:LIK}\\
\nonumber\\
&L^{'}_{s,g,a,k} = \left\{\begin{array}{l}
    Gamma(uc_{s,g,a,k} \vert \alpha_{y,g,a},\beta_{y,g,a}/c_{s,g,a}) \qquad if \; uc_{\cdot} = lc_{\cdot}\\\\
    \displaystyle \int_{x=lc_{s,g,a,k}}^{uc_{s,g,a,k}} Gamma(x \vert \alpha_{y,g,a},\beta_{y,g,a}/c_{s,g,a})dx \qquad if \; uc_{\cdot} > lc_{\cdot}    
      \end{array}\right.\\
\nonumber\\
&L^{''}_{s,g,a} = \mathcal{N}(pp_{s,g,a} \vert p_{y,g,a},pse_{s,g,a})
\end{align}$$
]


---
## `r top_icon("divide")`


---
## `r top_icon("check")`



---
## `r top_icon("chart-line")`



---
## `r top_icon("stop")`


---

 $$\require{color}\displaystyle 
\colorbox{#FFD1DC}{$Y = \beta_0 + \beta_1 X_1 + \ldots + \beta_n X_n$}$$

---
class: hide_logo
## References  

```{r, echo=FALSE, cache=FALSE, message=FALSE, results = 'asis'}
PrintBibliography(bib)
```


---
class: su-white hide_logo
<br/><br/>

.font80[
<p style ="font-size:400%; margin-bottom: -10px; margin-left: -5px;">Thank You!</p>
<div style = "margin-left:15px;">
`r icons::icon_style(icons::fontawesome("envelope"),fill = "#561a34")` [acois@sun.ac.za](mailto:acois@sun.ac.za)

ORCID: [0000-0002-7014-6510](https://orcid.org/0000-0002-7014-6510)

<p>Web of Science: [ AAK-8603-2020](https://www.webofscience.com/wos/author/rid/AAK-8603-2020)
]
<img src = "assets/sulogo_4.png" width = "270" style = "margin-top: 5px; margin-left:15px;"></img> 
</div>
<br/>

<div style = "text-align: right; position: fixed; right: 100px;">
<img src = "images/github.png" width = "85"></img> <br/>
.font70[
This presentation is available from: <br/>
<a href = "https://annibalecois,github.io/metaregression">https://annibaleaois.github.io/metaregression</a> <br/>
and the generating code from: <br/>
<a href = "https://github.com/annibalecois/metaregression">https://github.com/annibalecois/metaregression</a> <br/>
]
</div>

